---
title: "Pulse Rates"
author: "David Kane"
format: html
execute: 
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(rstanarm)
```


```{r}
x <- nhanes |> 
  select(pulse, gender) |> 
  drop_na() |> 
  filter(gender == "Female")
```


```{r}
summary(x)
```

What is the difference in pulse rate between two randomly selected female students in this class?

Preceptor Table is a table of data with rows and columns such that, if there is no missing data, it is easy to estimate the quantity of interest.

Wisdom is the first Cardinal Virtue in data science. Begin with the quantity of interest. Is that QoI a causal effect or simply a forecast? What Preceptor Table would allow you to calculate your QoI easily? Perform an exploratory data analysis (EDA) on the data you have. Is it valid to consider the data you have and the (theoretical) data from the Preceptor Table to have arisen out of the same population? If so, you may continue. If not, your attempt to estimate your QoI ends now.

Validity is the consistency, or lack there of, in the columns of our dataset and the corresponding columns in our Preceptor Table. In order to consider the two datasets to be drawn from the same population, the columns from one must be have a valid correspondence with the columns in the other. Validity, if true (or at least reasonable), allows us to construct the Population Table.


**The outcome in your Preceptor Table is not the same thing as the answer to your question.**

## Wisdom

predictive or causal
units
outcome
covariates
treatment
Preceptor Table
validity

One reason why validity fails.

Population Table

## Justice

Stability
Representativeness
Unconfoundedness


formula

## Courage

Estimate a model:

```{r}
fit_obj <- stan_glm(data = x, 
                    formula = pulse ~ 1, 
                    family = gaussian, 
                    refresh = 0,
                    seed = 9)

fit_obj
```



## Temperance


